---
title: 'DATA607 Assignment 2: SQL and R'
author: "James Williams"
output:
  pdf_document: default
  html_document:
    highlight: pygments
    theme: cerulean
---
## STEP 1: Load Movie_Rankings.sql into R dataframe

Data is stored here: https://github.com/jambawilliams/Movie_Rankings

There are some of the references I used:
https://www.r-bloggers.com/accessing-mysql-through-r/ 
https://cran.r-project.org/web/packages/RMySQL/RMySQL.pdf
http://www.sthda.com/english/wiki/ggplot2-scatter-plots-quick-start-guide-r-software-and-data-visualization

Connect R to MySQL and pull in the Movie Ratings table.

```{r load-data, eval=TRUE}
library(RMySQL)
mydb <-dbConnect(MySQL(), user='root', password='Sourpie7!', dbname='Assignment2', host='localhost')
rs <- dbSendQuery(mydb, "select * from Movie_Rankings")
data <- fetch(rs, n=-1)
```

## STEP 2: Explore Dataframe

Display the Movie Ratings table.

```{r display-data, eval=TRUE}
data
```


## STEP 3: Replace Null Values

Null values replaced with 0 since no ranking was orignally assigned.  This will allow us to pull summary statistics later.

```{r replace-null, eval=TRUE}
dbSendQuery(mydb, "UPDATE Movie_Rankings SET Snow_White = 0 where Snow_White is null")
dbSendQuery(mydb, "UPDATE Movie_Rankings SET Aladdin = 0 where Aladdin is null")
rs <- dbSendQuery(mydb, "select * from Movie_Rankings")
data_conditioned <- fetch(rs, n=-1)
data_conditioned
```


## STEP 4: Summary Statistics

```{r summary-statistics, eval=TRUE}
summary(data_conditioned)
```


## STEP 5: Graph Data Distribution

```{r box-plot, eval=TRUE}
library(reshape2)
library(ggplot2)
ggplot(melt(data_conditioned), aes(variable, value)) + geom_boxplot()
```